\setcounter{page}{1}
\chapter*{Acknowledgment}
\addcontentsline{toc}{chapter}{Acknowledgment}

We would like to take a moment to thank all of those involved in finalizing this work, whether directly or indirectly.

% Thanking the Incedo team
Our profound gratitude goes to the entire \textbf{Incedo Services GmbH team} for their warm welcome, invaluable support and for accompanying us throughout this wonderful journey.
Special thanks to our company supervisor and product owner \textbf{Mr. Manuel Schulze} who has been very involved with us almost daily throughout the long period of the internship, his trust in us has truly allowed us to come very far during this project.
We also appreciate \textbf{Wael Jaber} for initially showing us the ropes and for his continuous guidance.
Our deepest gratefulness also goes to \textbf{Mr. Robert Könitz} and \textbf{Mr. Tobias Schulze} for their huge efforts in contributing to our weekly mentoring sessions amongst other things, their input has truly been a huge source of knowledge for both of us and will be forevermore.

A very big thanks to our smart and kind professional supervisor \textbf{Mr. Anis Benna} for his efforts in showing us the best practices, his unwavering support, and for always being there to guide us through every step of the way. His wisdom and encouragement have been instrumental in our growth and success throughout this internship.
% Thanking the University supervisor
We also wish to acknowledge the great support of our university supervisor \textbf{Mrs. Asma Kerkeni} for her assistance, availability and valuable spot-on advice.
Her faith in us has truly allowed us to keep working on this project stress-free while confident this report will turn out better than initially intended.

Our heartfelt appreciation goes to the jury members who agreed to evaluate
our work and we hope they find it up to standard. We equally thank all
of the teachers of the  Higher Institute of Informatics and Mathematics of Monastir (ISIMM) who contributed to our education during these wonderful two and
a half years.
% \medskip
% \noindent We would also like to take this opportunity to express how joyful we are to keep working as official permanent team members of Incedo!

\newpage
