\thispagestyle{plain} % Remove header
\addcontentsline{toc}{chapter}{General Conclusion}
\section*{General Conclusion}

Throughout the period of our internship at Incedo Services GmbH, we dedicated ourselves to enhancing the Aermax platform by implementing new features, resolving existing issues, and improving overall functionality and user experience.

This project involved several key tasks, including developing a dynamic equipment list and creating a comprehensive reward system to engage users through achievements and XP/tokens. By adopting modern development methodologies and tools, we ensured that our solutions were both efficient and scalable.

The internship posed several challenges, including tight deadlines and the need to adapt to new technologies quickly. Despite these hurdles, the supportive and innovative environment at Incedo Services GmbH enabled significant learning and growth. We were able to expand our knowledge in fields such as microservices architecture, Kubernetes, RabbitMQ, and DevOps practices.

The team's encouragement of curiosity and continuous learning played a crucial role in motivating us to explore new technologies and enhance our technical skills. Some of the key technologies we became proficient in during this project include NestJS, Spring Boot, MongoDB, and various DevOps tools.

This internship has been an invaluable opportunity to apply our theoretical knowledge from the Higher Institute of Informatics and Mathematics of Monastir in a practical setting. It has also been a chance to develop new skills and gain experience in a professional environment. 

Working at Incedo has truly allowed us to shine, especially considering how very pleasant it was to communicate with the team, and we are extremely happy to have been recruited as permanent members of this wonderful family.

This internship has been a successful and enriching experience. We are eager to continue building on the foundation laid during this period and contribute significantly to the field of software development and DevOps.




